Evaluating Model Performances

### 2019-05-12 Scripts/comparing_tfbs_specific_models_with_all_annotations.Rmd
editted results scripts

# TFBS Specific Model Performances

## GM12878

### 10 kb

```{r}
#OC
##None
rfperf_gm12878_10kb_none_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/tfbs/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_10kb_none_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/tfbs/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_10kb_none_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/tfbs/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_gm12878_10kb_ros_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/tfbs/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_gm12878_10kb_ros_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/tfbs/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_gm12878_10kb_ros_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/tfbs/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_gm12878_10kb_rus_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/tfbs/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_gm12878_10kb_rus_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/tfbs/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_gm12878_10kb_rus_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/tfbs/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_gm12878_10kb_smote_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/tfbs/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_gm12878_10kb_smote_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/tfbs/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_gm12878_10kb_smote_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/tfbs/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878_tfbs <- data.frame(Resampling=rep(c(rep("None",3),
                                                    rep("ROS",3),
                                                    rep("RUS",3),
                                                    rep("SMOTE",3)),2),
                                       Predictor=rep(c("OC","OP","Distance"),8),
                                       Metric=c(rep("F1-Score",12), 
                                                rep("MCC",12)),
                                       Annotations=rep("TFBS Only",24)
                                       )

all_rfperfs_gm12878_tfbs$Predictor <- factor(all_rfperfs_gm12878_tfbs$Predictor, levels=c("OC", "OP", "Distance"))
all_rfperfs_gm12878_tfbs$Metric <- factor(all_rfperfs_gm12878_tfbs$Metric, levels=c("F1-Score", "MCC"))
all_rfperfs_gm12878_tfbs$Resampling <- factor(all_rfperfs_gm12878_tfbs$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))

all_rfperfs_gm12878_tfbs$Performance <- c(rfperf_gm12878_10kb_none_oc_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_none_op_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_none_dist_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_ros_oc_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_ros_op_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_ros_dist_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_rus_oc_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_rus_op_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_rus_dist_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_smote_oc_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_smote_op_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_smote_dist_tfbs[16,2], #f1

                                     rfperf_gm12878_10kb_none_oc_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_none_op_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_none_dist_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_ros_oc_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_ros_op_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_ros_dist_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_rus_oc_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_rus_op_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_rus_dist_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_smote_oc_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_smote_op_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_smote_dist_tfbs[15,2] #mcc

                                     )

@@

# All Annotations

## GM12878

### 10 kb

```{r}
#OC
##None
rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_gm12878_10kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_gm12878_10kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_gm12878_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_gm12878_10kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_gm12878_10kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_gm12878_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_gm12878_10kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_gm12878_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878 <- data.frame(Resampling=rep(c(rep("None",3),
                                                    rep("ROS",3),
                                                    rep("RUS",3),
                                                    rep("SMOTE",3)),2),
                                       Predictor=rep(c("OC","OP","Distance"),8),
                                       Metric=c(rep("F1-Score",12), 
                                                rep("MCC",12)),
                                       Annotations=rep("ALL Types",24)
                                       )

all_rfperfs_gm12878$Predictor <- factor(all_rfperfs_gm12878$Predictor, levels=c("OC", "OP", "Distance"))
all_rfperfs_gm12878$Metric <- factor(all_rfperfs_gm12878$Metric, levels=c("F1-Score", "MCC"))
all_rfperfs_gm12878$Resampling <- factor(all_rfperfs_gm12878$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))

all_rfperfs_gm12878$Performance <- c(rfperf_gm12878_10kb_none_oc[16,2], #f1
                                          rfperf_gm12878_10kb_none_op[16,2], #f1
                                          rfperf_gm12878_10kb_none_dist[16,2], #f1
                                          rfperf_gm12878_10kb_ros_oc[16,2], #f1
                                          rfperf_gm12878_10kb_ros_op[16,2], #f1
                                          rfperf_gm12878_10kb_ros_dist[16,2], #f1
                                          rfperf_gm12878_10kb_rus_oc[16,2], #f1
                                          rfperf_gm12878_10kb_rus_op[16,2], #f1
                                          rfperf_gm12878_10kb_rus_dist[16,2], #f1
                                          rfperf_gm12878_10kb_smote_oc[16,2], #f1
                                          rfperf_gm12878_10kb_smote_op[16,2], #f1
                                          rfperf_gm12878_10kb_smote_dist[16,2], #f1

                                     rfperf_gm12878_10kb_none_oc[15,2], #mcc
                                          rfperf_gm12878_10kb_none_op[15,2], #mcc
                                          rfperf_gm12878_10kb_none_dist[15,2], #mcc
                                          rfperf_gm12878_10kb_ros_oc[15,2], #mcc
                                          rfperf_gm12878_10kb_ros_op[15,2], #mcc
                                          rfperf_gm12878_10kb_ros_dist[15,2], #mcc
                                          rfperf_gm12878_10kb_rus_oc[15,2], #mcc
                                          rfperf_gm12878_10kb_rus_op[15,2], #mcc
                                          rfperf_gm12878_10kb_rus_dist[15,2], #mcc
                                          rfperf_gm12878_10kb_smote_oc[15,2], #mcc
                                          rfperf_gm12878_10kb_smote_op[15,2], #mcc
                                          rfperf_gm12878_10kb_smote_dist[15,2] #mcc

                                     )

@@

## Comparing 10 kb

```{r}
all_rfperfs_gm12878_allvtfbs <- rbind.data.frame(all_rfperfs_gm12878,all_rfperfs_gm12878_tfbs)
all_rfperfs_gm12878_allvtfbs$Annotations <- factor(all_rfperfs_gm12878_allvtfbs$Annotations, levels=c("ALL Types", "TFBS Only"))

ggplot(all_rfperfs_gm12878_allvtfbs,
       aes(x=Resampling, y=Performance, fill=Annotations)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid( ~ Predictor + Metric) +
  #xlab("") + ylab("") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Feature Space")+
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))
```

>>>>

# GM12878; smote; distance types

## 10kb

```{r}
mccdata_gm12878_10kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

			mccdata_gm12878_10kb <- rbind(mccdata_gm12878_10kb,
										  perfdata[15,2])

	}
}

@@

## 25kb

```{r}
mccdata_gm12878_25kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

			mccdata_gm12878_25kb <- rbind(mccdata_gm12878_25kb,
										  perfdata[15,2])

	}
}

## 50kb

```{r}
mccdata_gm12878_50kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

			mccdata_gm12878_50kb <- rbind(mccdata_gm12878_50kb,
										  perfdata[15,2])

	}
}

## 100kb

```{r}
mccdata_gm12878_100kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

			mccdata_gm12878_100kb <- rbind(mccdata_gm12878_100kb,
										  perfdata[15,2])

	}
}

# K562; smote; distance types

## 10kb

```{r}
mccdata_K562_10kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

			mccdata_K562_10kb <- rbind(mccdata_K562_10kb,
										  perfdata[15,2])

	}
}

## 25kb

```{r}
mccdata_K562_25kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

			mccdata_K562_25kb <- rbind(mccdata_K562_25kb,
										  perfdata[15,2])

	}
}

## 50kb

```{r}
mccdata_K562_50kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

			mccdata_K562_50kb <- rbind(mccdata_K562_50kb,
										  perfdata[15,2])

	}
}

## 100kb

```{r}
mccdata_K562_100kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("chromstates", "histones", "tfbs", "all")){
	  if(j %in% c("chromstates", "histones", "tfbs")){
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_",
									   j, 
									   ".rds"))
	  }else{
	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf.rds"))
	  }

			mccdata_K562_100kb <- rbind(mccdata_K562_100kb,
										  perfdata[15,2])

	}
}

@@

```{r}
all_rfperfs <- rbind.data.frame(mccdata_gm12878_10kb,
                                mccdata_gm12878_25kb,
                                mccdata_gm12878_50kb,
                                mccdata_gm12878_100kb,
                                mccdata_K562_10kb,
                                mccdata_K562_25kb,
                                mccdata_K562_50kb,
                                mccdata_K562_100kb)
all_rfperfs$CL <- c(rep("GM12878", length(mccdata_gm12878_10kb)*4), rep("K562", length(mccdata_K562_10kb)*4))
all_rfperfs$Resolution <- rep(c(rep("10 kb", 84),
                            rep("25 kb", 84),
                            rep("50 kb", 84),
                            rep("100 kb", 84)))
all_rfperfs$Annotation <- rep(c("CSS","HM","TFBS","Combined"),168)
all_rfperfs$Chromosome <- rep(c(rep("CHR1", 4),
                            rep("CHR2", 4),
                            rep("CHR3", 4),
                            rep("CHR4", 4),
                            rep("CHR5", 4),
                            rep("CHR6", 4),
                            rep("CHR7", 4),
                            rep("CHR8", 4),
                            rep("CHR10", 4),
                            rep("CHR11", 4),
                            rep("CHR12", 4),
                            rep("CHR13", 4),
                            rep("CHR14", 4),
                            rep("CHR15", 4),
                            rep("CHR16", 4),
                            rep("CHR17", 4),
                            rep("CHR18", 4),
                            rep("CHR19", 4),
                            rep("CHR20", 4),
                            rep("CHR21", 4),
                            rep("CHR22", 4)),8)

all_rfperfs$CL <- factor(all_rfperfs$CL, levels = c("GM12878", "K562"))
all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "CSS", "TFBS", "Combined"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_mcc <- all_rfperfs %>%
  dplyr::group_by(CL, Resolution, Annotation) %>%
  dplyr::summarise(MCC = mean(V1, na.rm = TRUE),
            MCCSD = sd(V1, na.rm = TRUE))

#GM12878
ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="GM12878"),], aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
  geom_bar(stat="identity", position = position_dodge()) +
  geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
  theme_minimal() +
  theme_bw()+
  #xlab("") + ylab("") + ylim(-.05,.5) +
  scale_fill_discrete(name="Annotation\nGroup")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                  angle = 45, 
                                  #margin = ggplot2::margin(t = 35),
                                  hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20))

#K562
ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="K562"),], aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
  geom_bar(stat="identity", position = position_dodge()) +
  geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
  theme_minimal() +
  theme_bw()+
  #xlab("") + ylab("") + ylim(-.05,.5) +
  scale_fill_discrete(name="Annotation\nGroup")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                  angle = 45, 
                                  #margin = ggplot2::margin(t = 35),
                                  hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20))
```

### 2019-05-12 Scripts/evaluating_model_performances.Rmd
editted results scripts

all_rfperfs_mcc <- all_rfperfs %>%
  group_by(CL, Resolution, Resampling, Predictor) %>%
  summarise(MCC = mean(V1, na.rm = TRUE),
            MCCSD = sd(V1, na.rm = TRUE))

>>>>

all_rfperfs_mcc <- all_rfperfs %>%
  dplyr::group_by(CL, Resolution, Resampling, Predictor) %>%
  dplyr::summarise(MCC = mean(V1, na.rm = TRUE),
            MCCSD = sd(V1, na.rm = TRUE))
